Fully structured proof theory for intuitionistic modal logics

### 2020-07-03 BicolorNS/aiml20/aiml20.tex
fixed all the virginialake commands

% Here you can include the standard packages you use.
% Try to avoid using non-standard packages.
% If you use a non-standard package you will have
% to submit it when you submit the final version of
% your paper.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{colonequals}

\usepackage[matrix,arrow]{xy}
\usepackage[noxy]{../../virginialake}
%\vlnosmallleftlabels
\vlnostructuressyntax

@@

\input{macros}

%\definecolor{notgreen}{rgb}{.1,.6,.1}
%\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
%\newcommand{\red}[1]{{\color{red}{#1}}}
%\newcommand{\blue}[1]{{\color{blue}{#1}}}
%\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
%\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
%
%%%% General
%
%\newcommand{\F}{\mathcal{F}}
%\newcommand{\M}{\mathcal{M}}
%%\newcommand{\G}{\mathcal{G}}
%
%\newcommand{\B}{\mathcal{B}}
%\newcommand{\Left}{\mathcal{L}}
%\newcommand{\Right}{\mathcal{R}}
%
%\newcommand*{\rel}{R}
%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
%\newcommand*{\invr}[1]{#1^\mathsf{inv}}
%
%\newcommand*{\orn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
%\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
%\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
%
%\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
%\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
%\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
%\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
%\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Logic
%\newcommand*{\ax}[1]{\mathsf{#1}}
%\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
%\newcommand*{\A}{\mathcal{A}}
%
%\newcommand{\force}[2]{#1\Vdash#2}
%\newcommand{\nforce}[2]{#1\nVdash#2}
%%
%\newcommand{\height}[1]{|#1|}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Systems
%\newcommand*{\K}{\mathsf{K}}
%\newcommand*{\IK}{\mathsf{IK}}
%\newcommand*{\lab}{\mathsf{lab}}
%\newcommand*{\n}{\mathsf{n}}
%
%%%% Connectives
%\newcommand*{\NOT}{\neg}
%\newcommand*{\AND}{\mathbin{\wedge}}
%\newcommand*{\TOP}{\mathord{\top}}
%\newcommand*{\OR}{\mathbin{\vee}}
%\newcommand*{\BOT}{\mathord{\bot}}
%\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
%
%\newcommand*{\BOX}{\mathord{\Box}}
%\newcommand*{\DIA}{\mathord{\Diamond}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Nested sequents
%\newcommand*\mdelim[3]{%
%	\mathopen{}\left#1%
%	#3%
%	\right#2\mathclose{}%
%}
%
%\makeatletter
%%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
%\newcommand*{\BR}{%
%\@ifnextchar\i{\br@two}{%
%\@ifnextchar\bgroup{\br@one}{% 
%}}}
%\newcommand*{\br@one}[1]{%
%\def\br@{#1}%
%\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
%}
%\newcommand*{\br@two}[3]{%
%\def\br@{#3}%
%\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
%}
%%
%\newcommand*{\bBR}{%
%\@ifnextchar\i{\bbr@two}{%
%\@ifnextchar\bgroup{\bbr@one}{% 
%}}}
%\newcommand*{\bbr@one}[1]{%
%\def\br@{#1}%
%\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
%}
%\newcommand*{\bbr@two}[3]{%
%\def\br@{#3}%
%\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
%}
%%
%%\newcommand*{\@makeoperator}[2]{
%%	\newcommand*{#1}{%
%%		\mathrm{#2}\mdelim{\lparen}{\rparen}
%%	}
%%}
%%%
%%\@makeoperator{\fm}{fm^{\n}}
%%\@makeoperator{\ofm}{fm^{\o}}
%%\@makeoperator{\hfm}{fm^{\h}}
%%%
%%\@makeoperator{\depth}{dp}
%%\@makeoperator{\rank}{rk}
%%\@makeoperator{\height}{ht}
%%\@makeoperator{\tree}{tree}
%%\@makeoperator{\graph}{graph}
%\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% contexts
%\makeatletter
%\newcommand*{\cxs}{%
%\@ifnextchar\i{\cxs@two}{%
%\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
%}}}
%\newcommand*{\cxs@one}[1]{%
%\def\cxs@{#1}%
%\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
%\cxs@one@decor%
%}
%\newcommand*{\cxs@two}[3]{%
%\def\cxs@{#3}%
%\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
%\cxs@one@decor%
%}
%\def\cxs@one@decor{%
%\@ifnextchar_{\cxs@one@sub}{%
%\@ifnextchar^{\cxs@one@sup}{%
%	\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
%		\@ifnextchar[{\cxs@one@arg}%]
%		\cxs}}}%
%}
%\def\cxs@one@sub_#1{_{#1}\cxs@one@decor}
%\def\cxs@one@sup^#1{^{#1}\cxs@one@decor}
%\def\cxs@one@arg[#1]{{#1}\cxs@one@decor}
%
%%% Change these as needed, but keep the \cx@continuation at the end
%\def\cx@delete@always#1{{#1}^{\ast}\cx@continuation}
%\def\cx@delete@right#1*{{#1}^{\star}\cx@continuation}
%\def\cx@delete@focus#1\f{{#1}^{\scriptscriptstyle\not{\langle}{\rangle}}\cx@continuation}
%
%\def\cx@delete@star#1*{%
%\@ifnextchar*{\cx@delete@right{#1}}{\cx@delete@always{#1}}%
%}
%
%\newcommand*{\@makecontextual}[2]{
%\newcommand*{#1}{%
%\@ifnextchar*{\cx@delete@star{#2}}{%
%	\@ifnextchar\f{\cx@delete@focus{#2}}{%
%		#2\cx@continuation}}%
%}%
%}
%\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}
%
%\@makecontextual{\Ex}{}
%
%\@makecontextual{\Cx}{\Gamma}
%\@makecontextual{\Dx}{\Delta}
%\@makecontextual{\Lx}{\Lambda}
%\@makecontextual{\Rx}{\Pi}
%
%\@makecontextual{\LLx}{\Omega}
%\@makecontextual{\RRx}{\Xi}
%\@makecontextual{\CCx}{\Sigma}
%\@makecontextual{\DDx}{\Theta}
%\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% intuitionistic
%\newcommand*{\rt}[1]{#1^\circ}
%\newcommand*{\lf}[1]{#1^\bullet}
%
%
%%%% Extracting symbols from MnSymbol 
%\DeclareFontFamily{U} {MnSymbolC}{}
%%
%\DeclareFontShape{U}{MnSymbolC}{m}{n}{
%<-6>  MnSymbolC5
%<6-7>  MnSymbolC6
%<7-8>  MnSymbolC7
%<8-9>  MnSymbolC8
%<9-10> MnSymbolC9
%<10-12> MnSymbolC10
%<12->   MnSymbolC12}{}
%\DeclareFontShape{U}{MnSymbolC}{b}{n}{
%<-6>  MnSymbolC-Bold5
%<6-7>  MnSymbolC-Bold6
%<7-8>  MnSymbolC-Bold7
%<8-9>  MnSymbolC-Bold8
%<9-10> MnSymbolC-Bold9
%<10-12> MnSymbolC-Bold10
%<12->   MnSymbolC-Bold12}{}
%%
%\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
%%
%\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
%\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
%
%
%%%% Labelled sequents
%\newcommand{\SEQ}{\Rightarrow}
%\newcommand*{\DD}{\mathcal{D}}
%%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
%%\newcommand*{\invr}[1]{#1^\bullet}
%%\newcommand*{\rel}{R}
%
%%%% Labelled rules
%\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
%\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
%\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
%%
%\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
%\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
%%
%\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
%\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
%
%\newcommand*{\labIKp}{\lab\IK_{\le}}
%\newcommand*{\nIKp}{\n\IK_{\le}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \begin{abstract}
  %We present a nested sequent system for intuitionistic modal logic in which we capture explicitly two relations: one for the accessibility relation associated with the Kripke semantics for normal modal logics (represented with one bracket in a formula or context) and one for the preorder relation associated with the Kripke semantics for intuitionistic logic (represented with two brackets in a formula or context).
  %
  We present a labelled sequent system and a nested sequent system for intuitionistic modal logics equipped with two relation symbols, one for the accesibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics for intuitionistic logic. Both systems are in close correspondence with birelational Kripke semantics for intuitionistic modal logic.
  \end{abstract}

@@

\begin{figure}
	\centering
	\fbox{
		\includegraphics[scale=.8]{fig-labIK}
	}		
	\caption{System $\labIKp$}
	\label{fig:labIK}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{
		\includegraphics[scale=.8]{fig-nIK}
	}		
\caption{System $\nIKp$}
\label{fig:nIK}
\end{figure}

@@

%In order to capture intuitionistic modal logics, we build a nested sequent system with the two relations explicitly: one of for the accessibility relation $\rel$ associated with the Kripke semantics for normal modal logics (represented with one bracket in the sequent) and one for the preorder relation $\le$ associated with the Kripje semantics for intuitionistic logic (represented with two brackets in the system).

%In the intuitionistic setting, the validity of a modal formula has to be defined using both the $\rel$ and the $\le$ relation as:
%$\force{\lb x}{\fm{\BOX A}}$ iff for all $\lb y$ and $\lb z$ s.t. $\futs xy$ and $\accs yz$, $\force{\lb z}{\fm{A}}$. Our system reflects exactly this definition in the rules introducing the $\BOX$-operator:
%
%\begin{center}
%	$\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf A, \Cx[2]}}}
%	\quad
%	\vlinf{\rrn\BOX}{}{\Cx{\rt{\BOX A}}}{\Cx{\bBR{\BR{\rt A}}}}$
%\end{center}
%
%\marianela{add F1 rule?}

@@

%\paragraph{Labelled}
%
%The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
%inference rule
%\begin{equation}
%\label{eq:Rtrans}
%\vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
%	\B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
%\end{equation}
%where $\B$ stands for a set of relational atoms, and $\Gamma$ and
%$\Delta$ for multi-sets of labelled formulas.

The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be axiomatised by the conjunction of the two versions of the $\ax 4$-axiom:\vspace*{-.2cm}
%\begin{equation*}
%\label{eq:4ax}
$$
\ax{4_{\BOX}}\colon\fm{\BOX A\IMP \BOX\BOX A}
\qquad\qquad\qquad
\ax{4_{\DIA}}\colon\fm{\DIA\DIA A\IMP\DIA A}
$$%\end{equation*}
%
which are equivalent in classical modal logic. 
%
However, in intuitionistic modal logic they are not and they can be added independently to the logic $\IK$. %(an intuitionistic version of $\K$). 
%
From~\cite{plotkin1986} we know they are in correspondance with the following frame conditions:\vspace*{-.2cm}
\begin{equation}
\label{eq:4frame}
\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{u}.\:\futs x{u}\AND\accs {u}z)
\quad
\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{u}.\:\futs z{u}\AND\accs {x}{u})
\end{equation}
%  \todo{add graphical representation of the conditions}
%$$
%\xymatrix{
%	u \ar@{.>}[drr]^R \\
%	x \ar@{.>}[u]^\le \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z
%}
%\qquad\qquad
%\xymatrix{
%	&& u  \\
%	x  \ar@{.>}[urr]^R \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z \ar@{.>}[u]^\le
%}
%$$
%respectively%, have already been studied in~\cite{plotkin:stirling:86}.

@@

\begin{center}
\includegraphics[scale=.8]{fig-trans}
\end{center}

%For example, you can add the following rule:
%$$\small
%\vlinf{\rn{trans}_\rel}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
%to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
%$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.

%In~\cite{plotkin1986}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
%%
%For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
%%\begin{center}
%($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
%%\end{center}

Incorporating the preorder symbol into the syntax, however,  allowed us~\cite{marin:morales:strassburger:hal} to %also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
%$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}, \Left \SEQ \Right}$}$$
%Consequently, we can easily 
translate the conditions in~\eqref{eq:4frame} into separate inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:%\vspace*{-.1cm}

\begin{center}
	\includegraphics[scale=.8]{fig-trans2}
\end{center}

%This allows us to define cut-free deductive systems for a wide range of logics that could not be treated before.

%Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin1986}.
%%
%These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.

@@

%The generalisation of these results to our fully structured framework is subject of ongoing study.

>>>>

% Here you can include the standard packages you use.
% Try to avoid using non-standard packages.
% If you use a non-standard package you will have
% to submit it when you submit the final version of
% your paper.

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb,latexsym}
\usepackage{stmaryrd}
\usepackage{colonequals}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Logic
\newcommand*{\ax}[1]{\mathsf{#1}}
\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
%\newcommand*{\A}{\mathcal{A}}
%
%\newcommand{\force}[2]{#1\Vdash#2}
%\newcommand{\nforce}[2]{#1\nVdash#2}
%%
%\newcommand{\height}[1]{|#1|}
\newcommand*{\rel}{R}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Connectives
\newcommand*{\NOT}{\neg}
\newcommand*{\AND}{\mathbin{\wedge}}
\newcommand*{\TOP}{\mathord{\top}}
\newcommand*{\OR}{\mathbin{\vee}}
\newcommand*{\BOT}{\mathord{\bot}}
\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}

\newcommand*{\BOX}{\mathord{\Box}}
\newcommand*{\DIA}{\mathord{\Diamond}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Systems
%\newcommand*{\K}{\mathsf{K}}
\newcommand*{\IK}{\mathsf{IK}}
%
\newcommand*{\lab}{\mathsf{lab}}
\newcommand*{\n}{\mathsf{n}}
%
\newcommand*{\labIKp}{\lab\IK_{\le}}
\newcommand*{\nIKp}{\n\IK_{\le}}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Nested sequents
%%%%%%%%%%%%%%%%%
%% intuitionistic annotations
\newcommand*{\rt}[1]{#1^\circ}
\newcommand*{\lf}[1]{#1^\bullet}
%
\newcommand*\mdelim[3]{%
	\mathopen{}\left#1%
	#3%
	\right#2\mathclose{}%
}
%
\makeatletter
%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
\newcommand*{\BR}{%
	\@ifnextchar\i{\br@two}{%
		\@ifnextchar\bgroup{\br@one}{% 
}}}
\newcommand*{\br@one}[1]{%
	\def\br@{#1}%
	\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
}
\newcommand*{\br@two}[3]{%
	\def\br@{#3}%
	\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
}
%
\newcommand*{\bBR}{%
	\@ifnextchar\i{\bbr@two}{%
		\@ifnextchar\bgroup{\bbr@one}{% 
}}}
\newcommand*{\bbr@one}[1]{%
	\def\br@{#1}%
	\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
}
\newcommand*{\bbr@two}[3]{%
	\def\br@{#3}%
	\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% contexts
\makeatletter
\newcommand*{\cxs}{%
	\@ifnextchar\i{\cxs@two}{%
		\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
}}}
\newcommand*{\cxs@one}[1]{%
	\def\cxs@{#1}%
	\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
	%\cxs@one@decor%
}
\newcommand*{\cxs@two}[3]{%
	\def\cxs@{#3}%
	\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
	%\cxs@one@decor%
}
%\def\cxs@one@decor{%
%\@ifnextchar_{\cxs@one@sub}{%
%\@ifnextchar^{\cxs@one@sup}{%
%\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
%	\@ifnextchar[{\cxs@one@arg}%]
%	\cxs}}}%
%}
%\def\cxs@one@sub_#1{_{#1}\cxs@one@decor}
%\def\cxs@one@sup^#1{^{#1}\cxs@one@decor}
%\def\cxs@one@arg[#1]{{#1}\cxs@one@decor}

%% Change these as needed, but keep the \cx@continuation at the end
%\def\cx@delete@always#1{{#1}^{\ast}\cx@continuation}
%\def\cx@delete@right#1*{{#1}^{\star}\cx@continuation}
%\def\cx@delete@focus#1\f{{#1}^{\scriptscriptstyle\not{\langle}{\rangle}}\cx@continuation}
%
%\def\cx@delete@star#1*{%
%\@ifnextchar*{\cx@delete@right{#1}}{\cx@delete@always{#1}}%
%}

\newcommand*{\@makecontextual}[2]{
	\newcommand*{#1}{%
		\@ifnextchar*{\cx@delete@star{#2}}{%
			\@ifnextchar\f{\cx@delete@focus{#2}}{%
				#2\cx@continuation}}%
	}%
}
\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}

\@makecontextual{\Cx}{\Gamma}
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%Rules
\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
%\newcommand*{\invr}[1]{#1^\mathsf{inv}}
%
\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}
\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Labelled sequents

\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
%
\newcommand{\SEQ}{\Rightarrow}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Left}{\mathcal{L}}
\newcommand{\Right}{\mathcal{R}}
%
\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Labelled rules
\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \begin{abstract}
  %We present a nested sequent system for intuitionistic modal logic in which we capture explicitly two relations: one for the accessibility relation associated with the Kripke semantics for normal modal logics (represented with one bracket in a formula or context) and one for the preorder relation associated with the Kripke semantics for intuitionistic logic (represented with two brackets in a formula or context).
  %
  We present a labelled sequent system and a nested sequent system for intuitionistic modal logics equipped with two relation symbols, one for the accessibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics for intuitionistic logic. Both systems are in close correspondence with the birelational Kripke semantics for intuitionistic modal logic.
  \end{abstract}

@@

\begin{figure}
	\centering
	\fbox{
		\includegraphics[scale=.9]{fig-labIK}
	}		
	\caption{System $\labIKp$}
	\label{fig:labIK}
\end{figure}

@@

\begin{figure}
	\centering
	\fbox{
		\includegraphics[scale=.9]{fig-nIK}
	}		
\caption{System $\nIKp$}
\label{fig:nIK}
\end{figure}

@@

@@

The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be axiomatised by the conjunction of the two versions of the $\ax 4$-axiom:\vspace*{-.2cm}
$$\small
\ax{4_{\BOX}}\colon\fm{\BOX A\IMP \BOX\BOX A}
\qquad\qquad\qquad
\ax{4_{\DIA}}\colon\fm{\DIA\DIA A\IMP\DIA A}
$$
%
which are equivalent in classical modal logic. 
%
However, in intuitionistic modal logic they are not and they can be added independently to the logic $\IK$. %(an intuitionistic version of $\K$). 
%
From~\cite{plotkin1986} we know they are in correspondance with the following frame conditions:\vspace*{-.2cm}
{\small
\begin{equation}
\label{eq:4frame}
\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{u}.\:\futs x{u}\AND\accs {u}z)
\quad
\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{u}.\:\futs z{u}\AND\accs {x}{u})
\end{equation}
}

@@

\begin{center}
\includegraphics[scale=.9]{fig-trans}
\end{center}

Incorporating the preorder symbol into the syntax, however,  allowed us~\cite{marin:morales:strassburger:hal} to 
translate the conditions in~\eqref{eq:4frame} into separate inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:%\vspace*{-.1cm}

\begin{center}
	\includegraphics[scale=.9]{fig-trans2}
\end{center}

@@
